---
title: "Analysis round 1"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(Microbial)
library(phyloseq)
library(magrittr)
library(microbiomeMarker)
load("F:/DataPaula/Esparanza/Asv_tables.RData")


```

```{r echo=FALSE}
vars <- asv_table.fam.relab %>%  sample_variables 
```


#### All samples
This is done on all samples, Organic and Conventional
```{r}
nsamples <- asv_table.treatment.fam.relab %>% sample_names() %>% length
paste("Number of samples:", nsamples)
```

```{r}
bray <- Permanova(asv_table.treatment.fam.relab, vars = c("Treatment"), method = 'bray')$aov.tab
uuni <- Permanova(asv_table.treatment.fam.relab, vars = c("Treatment"), method = 'uunifrac')$aov.tab
wuni <- Permanova(asv_table.treatment.fam.relab, vars = c("Treatment"), method = 'wunifrac')$aov.tab


results <- data.frame("R2_Bray"= bray$R2, "Pval_Bray"= bray$`Pr(>F)`,
           "R2_Unifrac" = uuni$R2, "Pval_Unifrac" = uuni$`Pr(>F)`,
           "R2_Wunifrac" = wuni$R2, "Pval_Wunifrac" = wuni$`Pr(>F)`) 

rownames(results) <- bray %>% rownames()
kable(results)

```
So the Treatment doesn't explains very little of the variance (Organic vs Conventional). Most likely there is a lot variation present within the Treatments, making them harder to separate from each other.

```{r}
sample_data(asv_table.treatment.fam.relab)[ , 2] <- sample_data(asv_table.treatment.fam.relab)[ ,1]

ordination <- ordinate(asv_table.treatment.fam.relab, method = "PCoA", distance = 'bray')
p1 <- plot_ordination(asv_table.treatment.fam.relab, ordination, type = 'samples', color = 'Treatment')
print(p1)
```
This plot more or less confirms that. Organic samples cluster relatively well (except for a few outliers), but conventional samples are all over the place. So in other words, conventional samples are some times more different from each other, than from organic samples. Therefore (not really, but it is a nice segue) we take a more detailed look at what makes conventional samples different from each other.


## conventional samples

```{r echo=FALSE}
nsamples <- asv_table.fam.relab %>% sample_names() %>% length
paste("Number of samples:", nsamples)
```



#### Permanova

If I leave DDEpp,DDEop+DDEpp+DDDopTDE+DDTop+DDDppTDE out, it works otherwise it doesn't ...
```{r echo=FALSE}
method = 'bray'
metadata <- as(sample_data(asv_table.fam.relab), "data.frame")
samp_dist <- distance(asv_table.fam.relab, method = method)
vars_perm <- paste(vars, collapse = '+')

bray <- adonis(samp_dist ~ PesticideConcentration+PesticideCompounds+Linuron+DimethenamidP+Cyromazine+Propamocarb+Flnicamid+Chloridazon+Metamitron+Cymoxanil+Azoxystrobin+Fluopicolide+BenthiavalicarbIsopropyl+Boscalid+Chlorpropham+Metribuzin+Desmedipham+Lenacil+Prosulfocarb+Penidmethalin+FenoxapropEthyl+Bixafen+Clethodim+Prothioconazole+ProthioconazoleDethio+tebuconazole+Metolachlor+Fenpropimorph+Bentazone+Adlrin+DDTpp+Glyphosate+AMPA, data = metadata, permutations = 999 )$aov.tab


method = 'uunifrac'
metadata <- as(sample_data(asv_table.fam.relab), "data.frame")
samp_dist <- distance(asv_table.fam.relab, method = method)
vars_perm <- paste(vars, collapse = '+')

uuni <- adonis(samp_dist ~ PesticideConcentration+PesticideCompounds+Linuron+DimethenamidP+Cyromazine+Propamocarb+Flnicamid+Chloridazon+Metamitron+Cymoxanil+Azoxystrobin+Fluopicolide+BenthiavalicarbIsopropyl+Boscalid+Chlorpropham+Metribuzin+Desmedipham+Lenacil+Prosulfocarb+Penidmethalin+FenoxapropEthyl+Bixafen+Clethodim+Prothioconazole+ProthioconazoleDethio+tebuconazole+Metolachlor+Fenpropimorph+Bentazone+Adlrin+DDTpp+Glyphosate+AMPA, data = metadata, permutations = 999 )$aov.tab


method = 'wunifrac'
metadata <- as(sample_data(asv_table.fam.relab), "data.frame")
samp_dist <- distance(asv_table.fam.relab, method = method)
vars_perm <- paste(vars, collapse = '+')

wuni <- adonis(samp_dist ~ PesticideConcentration+PesticideCompounds+Linuron+DimethenamidP+Cyromazine+Propamocarb+Flnicamid+Chloridazon+Metamitron+Cymoxanil+Azoxystrobin+Fluopicolide+BenthiavalicarbIsopropyl+Boscalid+Chlorpropham+Metribuzin+Desmedipham+Lenacil+Prosulfocarb+Penidmethalin+FenoxapropEthyl+Bixafen+Clethodim+Prothioconazole+ProthioconazoleDethio+tebuconazole+Metolachlor+Fenpropimorph+Bentazone+Adlrin+DDTpp+Glyphosate+AMPA, data = metadata, permutations = 999 )$aov.tab


results <- data.frame("R2_Bray"= bray$R2, "Pval_Bray"= bray$`Pr(>F)`,
           "R2_Unifrac" = uuni$R2, "Pval_Unifrac" = uuni$`Pr(>F)`,
           "R2_Wunifrac" = wuni$R2, "Pval_Wunifrac" = wuni$`Pr(>F)`) 

rownames(results) <- bray %>% rownames()
kable(results)


```
Most is explained by PesticideConcentration, some by PesticideCompounds and Metribuzin 


